Truthfulness Verification System

### 2011-04-13 trunk/proposal/paper.tex
Rearranged

\subsubsection{Les Paul invented the electric guitar}
The alternative units for this sentence are "Les Paul", "rickenbacker", "Gibson", "Leo", and "Lloyd". Now there is inherent ambiguity about the true inventor of the electric guitar. And Wikipedia does not specify rickenbacker as the inventor of electric guitar. Rather it specify Les Paul as the inventor in several places. Our algorithm unambigiously classify Les Paul as inventor of electric guitar in a similar way for the Sleepless in Seattle case described in the previous subsection.

%On reading the articles related above, there is no information that Rickenbacker actually inventing the electric guitar. He was a founding member of the Rickenbacker company that produces electric guitar. Les Paul on the other hand was a pioneer in designing and developing of what a prototype. Moreover, some of the categories attached with the Les Paul page are American musical instrument makers, Guitar makers, Inventors of musical instruments, National Inventors Hall of Fame inductees. In comparison Adolph Rickenbaker page has only one guitar related category - Guitar stubs, meaning the article is stuck in content.
\subsubsection{Luna 2 is the first spacecraft on the moon}
The alternative units for this sentence are "Luna 2", "Apollo", "Land", "Landing", and "Nasa". Our algorithm returns true for both Luna 2 and Apollo and return false for all others. Now, both Luna 2 and Apollo are in reality true considering the facts that Luna 2 was the first unmanned spacecraft and Apollo was the first manned spacecraft. Hence, we can't say one of the Luna 2 or Apollo as false if farther information is not given. So algorithm 2 can produce correct result for this sentence also.

>>>>

\subsubsection{Les Paul invented the electric guitar}
The alternative units for this sentence are "Les Paul", "rickenbacker", "Gibson", "Leo", and "Lloyd". Now there is inherent ambiguity about the true inventor of the electric guitar. On reading the articles related above, there is no information that Rickenbacker actually inventing the electric guitar. He was a founding member of the Rickenbacker company that produces electric guitar. Les Paul on the other hand was a pioneer in designing and developing of what a prototype. Moreover, some of the categories attached with the Les Paul page are American musical instrument makers, Guitar makers, Inventors of musical instruments, National Inventors Hall of Fame inductees. In comparison Adolph Rickenbaker page has only one guitar related category - Guitar stubs, meaning the article is stuck in content.

\subsubsection{Luna 2 is the first spacecraft on the moon}
The alternative units for this sentence are "Luna 2", "Apollo", "Land", "Landing", and "Nasa". Our algorithm returns true for both Luna 2 and Apollo and return false for all others. Now, both Luna 2 and Apollo are in reality true considering the facts that Luna 2 was the first unmanned spacecraft and Apollo was the first manned spacecraft. Hence, we can't say one of the Luna 2 or Apollo as false if farther information is not given. So algorithm 2 can produce correct result for this sentence also.
